Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2016-03-16 paper.tex
Resize LIR vs LUV figure
Paragraph on MC for varying durations

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.44]{lir_luv_sample.eps}
\caption{IR luminosity vs. emergent UV luminosity for the samples of dusty
and dust-poor galaxies.\label{lir_luv}}
\end{figure}

@@

The equations in \citet{kennicutt98} relate IR, emergent UV, and emergent
H$\alpha$ luminosities to star formation rates (SFRs).  We assume
that a galaxy's total SFR: (1) is the sum of its IR- and emergent UV-derived
SFR; and (2) equals the intrinsic (not emergent)
H$\alpha$-derived SFR.  The SFR equations are valid under different assumptions
for the duration of a galaxy's star formation episode.  Our assumptions will not
conflict with those of \citet{kennicutt98} if: (1) the SFR has been
constant for $\sim 10^{8}$ yr, so that the instantaneous H$\alpha$-derived SFR
equals the prolonged UV- and IR-derived SFRs; and (2) the dominant
source for the IR luminosity is not old stars or an active nucleus.

@@

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation (rederived in the same paper).  IRX
is IR luminosity divided by emergent UV luminosity.  This
relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.80}$
for the low-redshift
dust-poor galaxies.  If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.  We lack
uncertainties on any SFRs so we also perform a robust linear regression,
which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for the low-redshift
dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
SFR---we treat it as the dependent variable---in the weighted fit.  The relation
for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
low redshift.  In \S\ref{subsec:select} and \ref{sec:discuss} we explain why we
preface `inapplicable' with `seemingly.'

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.45}$
and \alephha~= \alephuv$^{0.66}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{Summary of regressions\label{regress}}
\tablehead{
\colhead{Sample} &
\colhead{$q$} &
\colhead{Std. error of $q$} &
\colhead{Residual std. error} &
\colhead{DOF}
}
\startdata
Low-z dust-poor & 0.799 & 0.094 & 6.0  & 13 \\
Low-z dusty     & 0.548 & 0.029 & 67.0 & 54 \\
High-z dusty    & 0.549 & 0.008 & 6.6  & 320
\enddata
\end{deluxetable}

@@

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  The \citet{reddy15} attenuation formula has
\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's SFR has been
constant for at least $10^{8}$ yr.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for three
reasons:
\begin{enumerate}
\item \citet{madau14} calculate conversion factors between luminosities and
star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.
\item \citet{madau14} use the models of \citet{conroy10} to calculate these
conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
using the conversion factor for the given UV escape fraction.
\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
$L_{\mathrm{IR}}$ are valid at different durations of the star formation
episode.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{The spread of true escape fractions that could contribute to
a given escape fraction if a galaxy's SFR has been constant for a
duration different from $10^{8}$ yr.  We assign the input
$f_{\mathrm{esc}}$ values to the conversion factors
between luminosity and SFR in \citet{kennicutt98}.  The UV and IR conversion
factors change as the duration of the star formation episode varies \citep{madau14}.
The durations for the points shown here range from $2\times10^{7}$ to
$1.5\times10^{10}$ yr.\label{spread}}
\end{figure}

@@

\begin{enumerate}
\item We measure H$\alpha$ line luminosities and limits, from
\emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
\item For each galaxy we determine \alephuv, the escape fraction at
0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
fraction, from the H$\alpha$ luminosity and the total star formation rate.
\item For the \citet{overzier11} sample of low-redshift dust-poor galaxies, we
recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
fractions: \alephha~= \alephuv$^{0.80}$.  Our nonstandard method for determining
H$\alpha$ escape fractions should be grossly correct.
\item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
that \alephha~= \alephuv$^{0.55}$.
\item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
\alephha~= \alephuv$^{0.55}$.  The dispersion about the best-fit relation is
large.
\item The interpretation of the results for dusty galaxies is unclear.  If we
assume that the \citet{calzetti00} attenuation formula applies to these
galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
\citet{price13}, and \citet{reddy15} and conflict with those of \citet{erb06}: \alephha~=
\alephuvha$^{1.6}$.  They study
samples comprising dust-poor and dusty galaxies.  Dusty galaxies have
nonuniform dust distributions.  However, dusty galaxies may disobey the
\citet{calzetti00} attenuation formula.
\item Measurements of the ratios of H$\alpha$ to H$\beta$ luminosities may
decrease the dispersion in the relation between H$\alpha$ and UV escape
fractions for dusty galaxies at $z \sim 1$.  If the dispersion is real, these
galaxies have diverse dust distributions.
\end{enumerate}

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.32]{lir_luv_sample.eps}
\caption{IR luminosity vs. emergent UV luminosity for the samples of dusty
and dust-poor galaxies.\label{lir_luv}}
\end{figure}

@@

Equations in \citet{kennicutt98} and \citet{madau14} relate IR, emergent UV,
and emergent H$\alpha$ luminosities to star formation rates (SFRs).  We multiply
UV luminosities by $2.68\times10^{-10}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$;
IR luminosities by $1.72\times10^{-10}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$;
and H$\alpha$ luminosities by
$3.02\times10^{-8}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$.
We assume that a galaxy's total SFR: (1) is the sum of its IR- and emergent
UV-derived SFR; and (2) equals the intrinsic (not emergent)
H$\alpha$-derived SFR.  The SFR equations are valid under different assumptions
for the duration of a galaxy's star formation episode.  Our assumptions will not
conflict with those of \citet{kennicutt98} and \citet{madau14} if: (1) the SFR
has been constant for 415 Myr, so that the instantaneous
H$\alpha$-derived SFR equals the prolonged UV- and IR-derived SFRs; and (2)
the dominant source for the IR luminosity is not old stars or an active nucleus.
We explore the uncertainty in our results due to variable durations of star
formation episodes in \S\ref{sec:discuss}.

@@

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation (rederived in the same paper).  IRX
is IR luminosity divided by emergent UV luminosity.  This
relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.56\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.77}$
for the low-redshift
dust-poor galaxies.  If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{XXXX}$.  We lack
uncertainties on any SFRs so we also perform a robust linear regression,
which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.53}$ for the low-redshift
dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
SFR---we treat it as the dependent variable---in the weighted fit.  The relation
for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
low redshift.  In \S\ref{subsec:select} and \ref{sec:discuss} we explain why we
preface `inapplicable' with `seemingly.'

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.54}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{XXXX}$
and \alephha~= \alephuv$^{XXXX}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = XXXX$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{Summary of regressions\label{regress}}
\tablehead{
\colhead{Sample} &
\colhead{$q$} &
\colhead{Std. error of $q$} &
\colhead{Residual std. error} &
\colhead{DOF}
}
\startdata
Low-z dust-poor & 0.766 & XXXX & XXXX & XXXX \\
Low-z dusty     & 0.532 & XXXX & XXXX & XXXX \\
High-z dusty    & 0.537 & XXXX & XXXX  & XXXX
\enddata
\end{deluxetable}

@@

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.1}$.  The \citet{reddy15} attenuation formula has
\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.3}$.
If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.54}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's SFR has been
constant for at least 415 Myr.  For example, if most
massive stars formed over 15 Myr instead of 415 Myr, we should multiply
$0.16 \times L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 56\% higher and the true IR SFR is 60\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for two
reasons:
\begin{enumerate}
\item We define the UV escape fraction as a function of UV- and IR-derived SFRs.
\citet{madau14} use the models of \citet{conroy10} to calculate
conversion factors between luminosities and SFRs.  The
conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We set aside the
circularity that results from using both these functions by fixing the UV
escape fraction in the SFR(IR)/$L_{\mathrm{IR}}$ function to the
given UV escape fraction.
\item Since SFR(IR)/$L_{\mathrm{IR}}$ is a function of more than duration of the
star formation episode, at a duration of 415 Myr most of the IR
conversion factors differ from our adopted value in \S\ref{sfrs}.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

We perform a second experiment to investigate the effect of episodes of constant
star formation rate with variable duration on the dispersion about the best-fit
relation.  For each high-redshift dusty galaxy we draw a random duration from a
uniform distribution with limits at 20 Myr and 15 Gyr.  We calculate the
galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
The IR conversion factor requires a UV escape fraction from one of the given
UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
fraction which is closest to the galaxy's UV escape fraction for a duration
of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
escape fractions for the random duration.  We perform a regression for the
sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
\ref{} shows the distribution of $q$ values from this process.  While the
$q$ values bounding the central 50\% of the sample encompass the range of $q$
values in Fig. \ref{}, we caution that this simulation involves many
assumptions.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{The spread of true escape fractions that could contribute to
a given escape fraction if a galaxy's SFR has been constant for a
duration different from 415 Myr.  We assign the input
$f_{\mathrm{esc}}$ values to the conversion factors
between luminosities and SFRs in \S\ref{sfrs}.  The UV and IR conversion
factors change as the duration of the star formation episode varies \citep{madau14}.
The durations for the points shown here range from $2\times10^{7}$ to
$1.5\times10^{10}$ yr.\label{spread}}
\end{figure}

@@

\begin{enumerate}
\item We measure H$\alpha$ line luminosities and limits, from
\emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
\item For each galaxy we determine \alephuv, the escape fraction at
0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
fraction, from the H$\alpha$ luminosity and the total star formation rate.
\item For the \citet{overzier11} sample of low-redshift dust-poor galaxies, we
recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
fractions: \alephha~= \alephuv$^{0.77}$.  Our nonstandard method for determining
H$\alpha$ escape fractions should be grossly correct.
\item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
that \alephha~= \alephuv$^{0.53}$.
\item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
\alephha~= \alephuv$^{0.54}$.  The dispersion about the best-fit relation is
large.
\item The interpretation of the results for dusty galaxies is unclear.  If we
assume that the \citet{calzetti00} attenuation formula applies to these
galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
\citet{price13}, and \citet{reddy15} and conflict with those of \citet{erb06}: \alephha~=
\alephuvha$^{1.6}$.  They study
samples comprising dust-poor and dusty galaxies.  Dusty galaxies have
nonuniform dust distributions.  However, dusty galaxies may disobey the
\citet{calzetti00} attenuation formula.
\item Measurements of the ratios of H$\alpha$ to H$\beta$ luminosities may
decrease the dispersion in the relation between H$\alpha$ and UV escape
fractions for dusty galaxies at $z \sim 1$.  If the dispersion is real, these
galaxies have diverse dust distributions.
\end{enumerate}
